Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidic System

### 2022-12-10 paper-kelompok/main.tex
Replace UI images with  a better-resolution ones

\title{Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System}

@@

\begin{abstract}
We have proposed a portable visible spectrophotometer with an ability to integrate with a particular digital microfluidic (DMF) system.
An interface, consisted of an LCD and a set of buttons, allowed users to gather and view measurement results in a continous manner.
The device had a dimension of 120 x 131 x 207 mm and had a weight of 832 g.
The device measured absorbance in the wavelength range of 400 to 700 nm with a resolution of 0.77 nm.
The device was tested by assessing the accuracy and repeatability of the transmission and wavelength measurements, as well as the wavelength resolution.
The results showed generally good performance compared with a research-grade commercial spectrophotometer.
\end{abstract}

@@

Current version of the spectrophotometer has some features as follows:
\begin{itemize}
    \item Concentration measurement of microdroplet samples 
    \item Absorbance measurement of samples based on wavelength characteristic 
    \item Able to work in visible spectrum (400 nm to 700 nm) 
    \item Able to be integrated with a digital microfluidic platform 
    \item The measurement results can be displayed on an LCD and stored 
    \item Portable (120 x 131 x 207 mm, 2 kg)
\end{itemize}

@@

\subsection{Power Subsystem}
The power subsystem enables the system to be activated by supplying power from the battery to the entire electrical circuit. 
The battery can be recharged with a 12V adapter whenever the battery voltage is insufficient. 
The power subsystem also provides information about the battery voltage value to be displayed to the user.

@@

The power from the adapter is converted into 8.4V (full capacity) using a charging module when charging is needed.
The power subsystem is activated when the user presses the power button for the first time—allowing the 8.4V to flow from the battery or the adapter(when charging) to the DC step-down module, giving 6V output to the microcontroller and other loads. 
If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.06]{lcd-spec.JPEG}}
    \caption{The display of the result pages of a spectrum-mode measurement}
    \label{lcd-spec}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.06]{lcd-conc.jpeg}}
    \caption{The display of the table page of a quantization-mode curve}
    \label{lcd-conc}
    \end{figure}

\section{Conclusions}
To support the study of spectrophotometry analysis in DMF platform, we have proposed the assembly of a portable visible spectrophotometer that can be integrated with a particular DMF system.
Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220 UV-Visible, Thermo Scientific™).
The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as reducing movable parts from the light path configuration.

\section*{Acknowledgement}
The authors thank Dr. Isa Anshori, from Department of Biomedical Engineering, and his research team for assistance with DMF integration and sample preparation.
This work was funded by the Department of Electrical Engineering, Institut Teknologi Bandung.

>>>>

\title{Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidic System}

@@

\begin{abstract}

\end{abstract}

@@

Current version of the spectrophotometer has some features as follows:
\begin{itemize}
    \item Concentration measurement of microdroplet samples 
    \item Absorbance measurement of samples based on wavelength characteristic 
    \item Able to work in visible spectrum (400 nm to 700 nm) 
    \item Able to be integrated with a digital microfluidic platform 
    \item The measurement results can be displayed on an LCD and stored 
    \item Portable (120 x 131 x 207 mm, 0.832 grams)
\end{itemize}

@@

\subsection{Power Subsystem}
The power subsystem enables the system to be activated by supplying power from the battery to the entire electrical circuit. The battery can be recharged easily whenever the battery voltage is insufficient. The power subsystem also provides information about the battery voltage value to be displayed to the user.

@@

The power subsystem is activated when the user presses the power button for the first time—allowing the power to flow to the microcontroller. The microcontroller will supply power to certain sub-blocks according to user input by adjusting the whether the battery voltage is sufficient based on a specified threshold. If the battery voltage value is below the threshold or the user presses the power button again, the power supply to the entire circuit will be cut off, and the system will be disabled.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.06]{lcd-spec.png}}
    \caption{The display of the result pages of a spectrum-mode measurement}
    \label{lcd-spec}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.06]{lcd-conc.png}}
    \caption{The display of the table page of a quantization-mode curve}
    \label{lcd-conc}
    \end{figure}

\section{Conclusions}
To support the study of spectrophotometry analysis in DMF platform, we describe the assembly of a portable spectrophotometer that can be integrated with a particular DMF system.
The portability makes on-the-go research processes easier.
Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220 UV-Visible, Thermo Scientific™).
The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as designing reducing movable parts from the light path configuration.

\section*{Acknowledgement}
This work was supported financially by Department of Electrical Engineering, Institut Teknologi Bandung.
The authors thank Mr. Isa Anshori, from Department of Biomedical Engineering, and his research team for assistance with DMF integration and sample preparation.

\section*{References}
